\section{State-of-the-Art}
The current tools readily available that provides scan\_for\_matches like 
functionality are RE2, Google's regular expression library due to 
how it handles alternations~\cite{re2java} as well as its linear running time and TRE, 
python's regex library and non-deterministic grep (NR-grep), since all three 
allows mismatches and supports backreferencing (though TRE does not allow 
backreferncing when mismatches are allowed). %TODO: CHECK BACKREF
 \subsection{RE2} %Google's RE engine
 RE2 is Google's regular expression library written in C++. It does not 
 support backreferencing, but claims to run faster if a pattern has a high degree 
 of alternations. Due to RE2's lack of support for backreferencing and mismatching, 
 it would be unable to properly reproduce scan\_for\_matches' functionality. 
 The project can be found on its github page: \url{https://github.com/google/re2}.
 \subsection{TRE} %Got both backtracking and backreferencing
 TRE was created by Ville Laurikari for his master's thesis in 
 2001\cite{LaurikariComplex}, and is a regular expression engine which supports 
 matching with mismatches and backreferences (though not when mismatches has 
 been specified). This makes, TRE an interesting candidate for modification in 
 order to simulate scan\_for\_matches functionality (see Section~\ref{tre}).
 \subsection{Python's Regex Library} %Group ref. instead of backref
 The python module regex~\cite{pythonregex} is an alternative regular expression 
 module to the native python module re created by Matt Barnett. It allows the 
 specification of mismatches in its search terms, however because of the lack 
 of theoretical documentation pertaining to the module and the nature of 
 the language the module was written for, we didn't see the regex library as 
 a potential alternative for scan\_for\_matches. 
 \subsection{NR-grep}
 NR-grep~\cite{Navarro00nr-grep:a} is a pattern matching tool written 
 in C by Gonzalo Navarro in 2000. It allows backreferences as well as mismatching, 
 and would have been a candidate alongside TRE had 
 we learned about it earlier. However, we learned about the tool 
 late in the process, and did not have sufficient time to include it in this thesis.
